### 2015-02-22 fundamentals/intro.tex
updates language between dynamic and static simulators. now all language points to dynamic as in time-stepping, facilities, etc.

The cardinal purpose of a nuclear fuel cycle simulator is to calculate the
time- and facility-dependent mass flow through all or part the fuel cycle.
Historically, nuclear fuel cycle simulators have calculated fuel cycle mass
balances and performance metrics derived from them using software ranging from
ad hoc spreadsheet-driven flow calculators to highly specialized system
dynamics modeling platforms. To date, current tools are often static rather
than dynamic, rigid rather than flexible, fleet-based rather than discrete, or
privately distributed rather than open source. Each of these choices presents a
challenge to modeling fidelity, generality, efficiency, robustness, and
scientific transparency.

@@

\Cyclus, therefore, is a dynamic, agent-based model, which employs a modular
architecture, an open development process, discrete agents, discrete time, and
arbitrarily detailed isotopic resolution of materials. Dynamic nuclear fuel
cycle analysis more realistically supports a range of simulation goals than
static analysis \cite{piet_dynamic_2011}. Similarly, experience in the broader
field of systems analysis indicates that agent-based modeling enables more
flexible simulation control, without loss of generality
\cite{macal_agent-based_2010}. Finally, openness allows cross-institutional
collaboration, increases software robustness \cite{cohen_modern_2010}, and
cultivates an ecosystem of modeling and calculation options. Comprised of
flexible, interchangeable models of fuel cycle components with varying scope,
depth and fidelity, this ecosystem allows users and developers to customise
\Cyclus to analyze the cases that are of interest to them, rather than those
the simulator was originally developed to address.  The fundamental concepts of
the \Cyclus nuclear fuel cycle simulator capture these modern insights so that
novel challenges in nuclear fuel cycle analysis can be better addressed.

>>>>

The cardinal purpose of a dyamic nuclear fuel cycle simulator is to calculate
the time- and facility-dependent mass flow through all or part the fuel cycle.
Dynamic nuclear fuel cycle analysis more realistically supports a range of
simulation goals than static analysis \cite{piet_dynamic_2011}. Historically,
dynamic nuclear fuel cycle simulators have calculated fuel cycle mass balances
and performance metrics derived from them using software ranging from ad hoc
spreadsheet-driven flow calculators to highly specialized system dynamics
modeling platforms. To date, current tools are often rigid rather than flexible,
fleet-based rather than discrete, or privately distributed rather than open
source. Each of these choices presents a challenge to modeling fidelity,
generality, efficiency, robustness, and scientific transparency.

@@

\Cyclus, therefore, is a dynamic, agent-based model, which employs a modular
architecture, an open development process, discrete agents, discrete time, and
arbitrarily detailed isotopic resolution of materials. Experience in the broader
field of systems analysis indicates that agent-based modeling enables more
flexible simulation control, without loss of generality
\cite{macal_agent-based_2010}. Furthermore, openness allows cross-institutional
collaboration, increases software robustness \cite{cohen_modern_2010}, and
cultivates an ecosystem of modeling and calculation options. Comprised of
flexible, interchangeable models of fuel cycle components with varying scope,
depth and fidelity, this ecosystem allows users and developers to customise
\Cyclus to analyze the cases that are of interest to them, rather than those the
simulator was originally developed to address.  The fundamental concepts of the
\Cyclus nuclear fuel cycle simulator capture these modern insights so that novel
challenges in nuclear fuel cycle analysis can be better addressed.
